Matching Bullets

### 2015-11-24 imaging-paper.Rnw
Images for steps of Loess fitting

\begin{figure}
<<fixedX, dependson='data', echo=FALSE, warning=FALSE, message=FALSE, fig.height=2, fig.width=6, out.width='\\linewidth'>>=
library(RColorBrewer)
library(ggplot2)
library(scales)
library(dplyr)
library(x3pr)
library(x3prplus)

@@

\begin{enumerate}
    \item Fix an x coordinate value.
    \item Remove values from $y \in \{0, 100\}$ and $y \in \{900, 1000\}$.
    \item For each y value from 100 to 900, compute a rolling average to smooth out any deviations occurring near the minimums.
    \item Determine the minimum in the first half (corresponding to the left groove) and the minimum in the right half (corresponding to the right groove)
    \item Remove all y values below the minimum and above the maximum
\end{enumerate}

@@

<<loess_fit, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Loess fit for part 1 of bullet 1', fig.pos='H', message=FALSE>>=
br111 <- get_bullet(file.path("GitHub", "x3prproto", "images", "Hamby252_3DX3P1of2", "Br1 Bullet 1-1.x3p"))
br111.groove <- get_grooves(br111)

my.loess <- fit_loess(br111, br111.groove)

@@

<<loess_resid, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Loess fit residuals for part 1 of bullet 1', fig.pos='H'>>=
my.loess <- fit_loess(br111, br111.groove)

@@

\begin{figure}
<<barrel2, echo=FALSE, fig.width = 7.5, fig.height=7.5, out.width='\\linewidth', warning=FALSE>>=
library(grid)
library(gridExtra)
thresholds <- seq(0.3, 1.5, by = 0.05)
list_of_matches <- lapply(19:24, function(i) {
  lof <- processBullets(paths = images[c(15,i)], x = 100)
  lof <- bulletSmooth(lof)

>>>>

\begin{figure}
<<fixedX, dependson='data', echo=FALSE, warning=FALSE, message=FALSE, fig.height=2, fig.width=6, out.width='\\linewidth'>>=
library(RColorBrewer)
library(ggplot2)
library(scales)
library(dplyr)
library(x3pr)
library(x3prplus)
library(grid)
library(gridExtra)
library(zoo)

@@

\begin{enumerate}
    \item Fix an x coordinate value. (Top panel of Figure \ref{fig:loess_step12})
    \item Remove values from $y \in \{0, 100\}$ and $y \in \{900, 1000\}$. (Bottom panel of Figure \ref{fig:loess_step12})
    \item For each y value from 100 to 900, compute a rolling average to smooth out any deviations occurring near the minimums. (Top panel of Figure \ref{fig:loess_step34})
    \item Determine the minimum in the first half (corresponding to the left groove) and the minimum in the right half (corresponding to the right groove) (Bottom panel of Figure \ref{fig:loess_step34})
    \item Remove all y values below the minimum and above the maximum (Figure \ref{fig:loess_step5})
\end{enumerate}

@@

<<loess_step12, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Steps 1 and 2 of the Loess fit algorithm. The top panel is a plot of height values for part 1 of bullet 1 across different values of y, with x held constant at 243.75. The bottom panel is the same plot, but with the first and last 100 y values trimmed.', fig.pos='H', message=FALSE>>=
br111_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-1.x3p", sep = "/"))

p1 <- qplot(y, value, data = br111_bullet) + theme_bw()
p2 <- qplot(y, value, data = tail(head(br111_bullet, n = -100), n = -100)) + theme_bw()

grid.arrange(p1, p2, nrow = 2)
@

<<loess_step34, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Steps 3 and 4 of the Loess fitting algorithm. The top panel is a plot of the smoothed height values, and the bottom panel is a plot of the detected minimums.', fig.pos='H', message=FALSE>>=
subdata <- tail(head(br111_bullet, n = -100), n = -100)
subdata$smoothed <- c(rep(NA, 10), rollapply(subdata$value, 21, function(x) mean(x, na.rm = TRUE)), rep(NA, 10))
p3 <- qplot(y, smoothed, data = tail(head(subdata, n = -10), n = -10)) + theme_bw()

curdata <- tail(head(subdata, n = -10), n = -10)
min.left <- which.min(curdata$value[1:(length(curdata$value) %/% 2)])
min.right <- which.min(curdata$value[(length(curdata$value) %/% 2):length(curdata$value)])

p4 <- qplot(data=curdata, y, value) +
        theme_bw() +
        geom_vline(xintercept = curdata$y[min.left], colour = "red") +
        geom_vline(xintercept = curdata$y[min.right + (length(curdata$y) %/% 2)], colour = "blue")

grid.arrange(p3, p4, nrow = 2)
@

<<loess_step5, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Step 5 of the Loess fitting algorithm. The plot shows the result after trimming values below the first minimum, and above the second minimum.', fig.pos='H', message=FALSE>>=
final.dat <- subset(curdata, y > curdata$y[min.left + 5] & y < curdata$y[min.right + (length(curdata$y) %/% 2) - 5])

qplot(data=final.dat, y, value) +
    theme_bw()
@

<<loess_fit, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Loess fit for part 1 of bullet 1', fig.pos='H', message=FALSE>>=

br111.groove <- get_grooves(br111_bullet)

my.loess <- fit_loess(br111_bullet, br111.groove)

@@

<<loess_resid, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Loess fit residuals for part 1 of bullet 1', fig.pos='H'>>=
my.loess <- fit_loess(br111_bullet, br111.groove)

@@

\begin{figure}
<<barrel2, echo=FALSE, fig.width = 7.5, fig.height=7.5, out.width='\\linewidth', warning=FALSE>>=
thresholds <- seq(0.3, 1.5, by = 0.05)
list_of_matches <- lapply(19:24, function(i) {
  lof <- processBullets(paths = images[c(15,i)], x = 100)
  lof <- bulletSmooth(lof)
